Amazon in Presidential Speeches in Brazil: data exploration for contexts

### 2022-02-07 draft November 2021/11112021_Sposito_and_SilvaMuller_DRAFT.Rmd

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author:
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
date: "11/11/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

>>>>

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author:
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
date: "11/11/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

ggplot(freq_year, aes(x = year)) +
    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
      labs(x = "",
       y = "Relative share of speeches per year",
       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
       subtitle = "Compared to annual deforestation rates since 1988",
       color = "")+
       theme(legend.position ="bottom")+
        scale_colour_manual(values=cbbPalette)

### 2022-02-07 others/data_exploration_1_full text.Rmd

---
title: "Amazon in Presidential Speeches in Brazil (Inductive Analysis)"
author: "Henrique Sposito"
date: "10/15/2021"
output: html_document
---

@@

```{r amazon, warning=FALSE, message=FALSE}
library(dplyr)
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
# BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text, level = "sentences")
# This takes a while to run, but we get context for all matches in dataset as a variable in dataset!
Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches,
                                 grepl("Amazôn|Amazon|amazôn|amazon", text))
# 861 speeches mention words related to Amazon
summary(as.factor(Amazon_speeches$president)) # Frequency by president
plot(Amazon_speeches$year, as.factor(Amazon_speeches$year), type = "b",
     main = "Presidential Speeches about the Amazon in Time in Brazil",
     xlab = "Year", ylab = "Frequency") # simple plot, but interesting!
```

@@

```{r sentiment, warning=FALSE, message=FALSE}
library(ggplot2)
library(stringr)
# library(poldis)
# Load internal sentiment dictionaries from poldis
Afinn_pt <- poldis:::Afinn_pt
nrc_portuguese <- poldis:::nrc_portuguese

@@

>>>>

---
title: "Amazon in Presidential Speeches in Brazil: data exploration for full texts"
author: "Henrique Sposito and Livio Silva-Muller"
date: "10/15/2021"
output: html_document
---

@@

```{r amazon, warning=FALSE, message=FALSE}
library(dplyr)
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches,
                                 grepl("Amazôn|Amazon|amazôn|amazon", text))
# 861 speeches mention words related to Amazon
summary(as.factor(Amazon_speeches$president)) # Frequency by president
plot(Amazon_speeches$year, as.factor(Amazon_speeches$year), type = "b",
     main = "Presidential Speeches about the Amazon in Time in Brazil",
     xlab = "Year", ylab = "Frequency") # simple plot, but interesting!
```

@@

```{r sentiment, warning=FALSE, message=FALSE}
library(ggplot2)
library(stringr)
# library(poldis)

# Load internal sentiment dictionaries from poldis
Afinn_pt <- poldis:::Afinn_pt
nrc_portuguese <- poldis:::nrc_portuguese

@@

This is where I stop since, overall, this appears not to be very helpful ...
But how about we try the a similar script with only the matches themselves instead of full texts?

### 2022-02-07 others/data_exploration_2_context.Rmd

```{r narratives, warning=FALSE, message=FALSE}
# Create the dictionary
sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado") # This appears harder to operationalize than others...

>>>>

```{r narratives, warning=FALSE, message=FALSE}
library(tidyr)

# Create the dictionary
sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado") # This appears harder to operationalize than others...
